%
%	Low-Level Block Operations
%
%   $Id: Blit.tex,v 4.1.2.1.2.1 1999/07/20 16:16:14 geert Exp $
% 
%   Copyright (C) 1996-1999 Department of Computer Science, K.U.Leuven, Belgium
% 
%   This program is free software; you can redistribute it and/or modify
%   it under the terms of the GNU General Public License as published by
%   the Free Software Foundation; either version 2 of the License, or
%   (at your option) any later version.
% 
%   This program is distributed in the hope that it will be useful,
%   but WITHOUT ANY WARRANTY; without even the implied warranty of
%   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%   GNU General Public License for more details.
% 
%   You should have received a copy of the GNU General Public License
%   along with this program; if not, write to the Free Software
%   Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
%

\begin{manpage}{\libtitle}{Blit}{$ $Revision: 4.1.2.1.2.1 $ $}

\subtitle{Name}
    Blit --- Low-level block operations

% -----------------------------------------------------------------------------

\subtitle{Description}
    This package provides some frequently used low-level block operations.
    All functions are template functions, allowing for different operand types.

% -----------------------------------------------------------------------------

\subtitle{Declaration}
    \needsinclude{Blit.h}

% -----------------------------------------------------------------------------

\subtitle{Operations}

\function{void Copy(const~Type$\ast$ src, Type$\ast$ dst, u\_int len)}
    Copy \name{len} objects from \name{src} to \name{dst}.

\function{void Copy(const~Type$\ast$ src, Type$\ast$ dst)}
    Copy the object pointed to by \name{src} to \name{dst}.

\function{void Fill(Type$\ast$ dst, u\_int len, Type value)}
    Fill \name{len} objects pointed to by \name{dst} with \name{value}.

\function{void Clear(Type$\ast$ dst, u\_int len)}
    Clear \name{len} objects pointed to by \name{dst}.

\function{void Clear(Type$\ast$ dst)}
    Clear the object pointed to by \name{dst}.

\function{void CopyRect(const~Type$\ast$ src, u\_int sw, Type$\ast$ dst,
			u\_int dw, u\_int cols, u\_int rows)}
    Copy a rectangular block of objects with \name{cols} columns and
    \name{rows} rows from \name{src} to \name{dst}. The source area has
    \name{sw} columns, while the destination area has \name{dw} columns.

\function{void CopyRect(const~Type$\ast$ src, u\_int sw, u\_int sx, u\_int sy,
			Type$\ast$ dst, u\_int dw, u\_int dx, u\_int dy,
			u\_int cols, u\_int rows)}
    Copy a rectangular block of objects with \name{cols} columns and
    \name{rows} rows from \name{src} at position (\name{sx}, \name{sy}) to
    \name{dst} at position (\name{dx}, \name{dy}). The source area has
    \name{sw} columns, while the destination area has \name{dw} columns.

\function{void FillRect(Type$\ast$ dst, u\_int dw, u\_int cols, u\_int rows,
			Type value)}
    Fill a rectangular block of objects with \name{cols} columns and
    \name{rows} rows, pointed to by \name{dst} with \name{value}. The
    destination area has \name{dw} columns.

\function{void FillRect(Type$\ast$ dst, u\_int dw, u\_int dx, u\_int dy,
			u\_int cols, u\_int rows, Type value)}
    Fill a rectangular block of objects with \name{cols} columns and
    \name{rows} rows, pointed to by \name{dst} at position (\name{dx},
    \name{dy}) with \name{value}. The destination area has \name{dw} columns.

\function{void ClearRect(Type$\ast$ dst, u\_int dw, u\_int cols, u\_int rows)}
    Clear a rectangular block of objects with \name{cols} columns and
    \name{rows} rows, pointed to by \name{dst}. The destination area has
    \name{dw} columns.

\function{void ClearRect(Type$\ast$ dst, u\_int dw, u\_int dx, u\_int dy,
			 u\_int cols, u\_int rows)}
    Clear a rectangular block of objects with \name{cols} columns and
    \name{rows} rows, pointed to by \name{dst} at position (\name{dx},
    \name{dy}). The destination area has \name{dw} columns.

% -----------------------------------------------------------------------------

\subtitle{Revision}
    \rev{Blit.h,v 4.0 1997/05/05 09:46:21 geert Exp}

\end{manpage}
