%
%	Stream Class
%
%   $Id: Stream.tex,v 4.1.2.3.2.1 1999/07/20 16:16:16 geert Exp $
% 
%   Copyright (C) 1996-1999 Department of Computer Science, K.U.Leuven, Belgium
% 
%   This program is free software; you can redistribute it and/or modify
%   it under the terms of the GNU General Public License as published by
%   the Free Software Foundation; either version 2 of the License, or
%   (at your option) any later version.
% 
%   This program is distributed in the hope that it will be useful,
%   but WITHOUT ANY WARRANTY; without even the implied warranty of
%   MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%   GNU General Public License for more details.
% 
%   You should have received a copy of the GNU General Public License
%   along with this program; if not, write to the Free Software
%   Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
%

\begin{manpage}{\libtitle}{Stream}{$ $Revision: 4.1.2.3.2.1 $ $}

\subtitle{Name}
    Stream --- Input/output with support for compression

% -----------------------------------------------------------------------------

\subtitle{Description}
    Flexible file storage with support for simple data compression.
    If a filename ends with \texttt{.gz} it will be compressed/decompressed
    automatically using \name{gzip}.

\function{Stream()}
    Create a file handler for a stream.

\function{Stream(const~char$\ast$ name, const~char$\ast$ type = "r")}
    Create a file handler for a stream and open it.

% -----------------------------------------------------------------------------

\subtitle{Declaration}
    \needsinclude{Storage.h}

% -----------------------------------------------------------------------------

\subtitle{Public \\ Operations}

\function{void Read(u8$\ast$ x, u\_int cnt = 1)}
\function{void Read(u16$\ast$ x, u\_int cnt = 1)}
\function{void Read(u32$\ast$ x, u\_int cnt = 1)}
\function{void Read(u64$\ast$ x, u\_int cnt = 1)}
\function{void Read(s8$\ast$ x, u\_int cnt = 1)}
\function{void Read(s16$\ast$ x, u\_int cnt = 1)}
\function{void Read(s32$\ast$ x, u\_int cnt = 1)}
\function{void Read(s64$\ast$ x, u\_int cnt = 1)}
\function{void Read(f32$\ast$ x, u\_int cnt = 1)}
\function{void Read(f64$\ast$ x, u\_int cnt = 1)}
    Read \name{cnt} elements from the stream.

\function{void Write(const~u8$\ast$ x, u\_int cnt = 1)}
\function{void Write(const~u16$\ast$ x, u\_int cnt = 1)}
\function{void Write(const~u32$\ast$ x, u\_int cnt = 1)}
\function{void Write(const~u64$\ast$ x, u\_int cnt = 1)}
\function{void Write(const~s8$\ast$ x, u\_int cnt = 1)}
\function{void Write(const~s16$\ast$ x, u\_int cnt = 1)}
\function{void Write(const~s32$\ast$ x, u\_int cnt = 1)}
\function{void Write(const~s64$\ast$ x, u\_int cnt = 1)}
\function{void Write(const~f32$\ast$ x, u\_int cnt = 1)}
\function{void Write(const~f64$\ast$ x, u\_int cnt = 1)}
    Write \name{cnt} elements to the stream.

\function{void Read(u8\& x)}
\function{void Read(u16\& x)}
\function{void Read(u32\& x)}
\function{void Read(u64\& x)}
\function{void Read(s8\& x)}
\function{void Read(s16\& x)}
\function{void Read(s32\& x)}
\function{void Read(s64\& x)}
\function{void Read(f32\& x)}
\function{void Read(f64\& x)}
    Read the element \name{x} from the stream.

\function{void Write(const~u8\& x)}
\function{void Write(const~u16\& x)}
\function{void Write(const~u32\& x)}
\function{void Write(const~u64\& x)}
\function{void Write(const~s8\& x)}
\function{void Write(const~s16\& x)}
\function{void Write(const~s32\& x)}
\function{void Write(const~s64\& x)}
\function{void Write(const~f32\& x)}
\function{void Write(const~f64\& x)}
    Write the element \name{x} to the stream.

\function{void Puts(const~char$\ast$ s)}
    Write the string \name{s} to the stream.

\function{void Printf(const~char$\ast$ fmt, ...)}
    Format and write a string to the stream.

% -----------------------------------------------------------------------------

\subtitle{Virtual \\ Operations}

\function{virtual~void Open(const~char$\ast$ name,
			    const~char$\ast$ mode = "r")}
    Open the stream using filename \name{name} and mode \name{mode}.

\function{virtual~void Close(void)}
    Close the stream.

\function{virtual~void RawRead(void$\ast$ data, int size)}
\function{virtual~void RawWrite(const~void$\ast$ data, int size)}
    Read or write a raw block of memory from or to the stream. Note that no
    endianness conversion will be done!

% -----------------------------------------------------------------------------

\subtitle{Endiannes}
    All I/O operations are done using network byte order, i.e.\ most
    significant byte first or big endian.

% -----------------------------------------------------------------------------

\separator

\subtitle{See Also}
    The \name{gzip} command.

% -----------------------------------------------------------------------------

\separator

\subtitle{Revision}
     \rev{Storage.C,v 4.0.2.2 1999/07/20 13:14:18 geert Exp}
     \rev{Storage.h,v 4.0.2.2 1999/07/20 13:14:16 geert Exp}

\end{manpage}
